---
title: "hw6"
output: github_document
date: "2023-11-29"
---

```{r}
library(tidyverse)
library(p8105.datasets)
library(modelr)
library(mgcv)

set.seed(1)
```

# Problem 1 

In the data cleaning code below we create a `city_state` variable, change `victim_age` to numeric, modifiy victim_race to have categories white and non-white, with white as the reference category, and create a `resolution` variable indicating whether the homicide is solved. Lastly, we filtered out the following cities: Tulsa, AL; Dallas, TX; Phoenix, AZ; and Kansas City, MO; and we retained only the variables `city_state`, `resolution`, `victim_age`, `victim_sex`, and `victim_race`.

```{r q1_data_cleaning}
homicide_df = 
  read_csv("data/homicide-data.csv", na = c("", "NA", "Unknown")) |> 
  mutate(
    city_state = str_c(city, state, sep = ", "),
    victim_age = as.numeric(victim_age),
    resolution = case_when(
      disposition == "Closed without arrest" ~ 0,
      disposition == "Open/No arrest"        ~ 0,
      disposition == "Closed by arrest"      ~ 1)
  ) |> 
  filter(victim_race %in% c("White", "Black")) |> 
  filter(!(city_state %in% c("Tulsa, AL", "Dallas, TX", "Phoenix, AZ", "Kansas City, MO"))) |> 
  select(city_state, resolution, victim_age, victim_sex, victim_race)
```
Next we fit a logistic regression model using only data from Baltimore, MD. We model `resolved` as the outcome and `victim_age`, `victim_sex`, and `victim_race` as predictors. We save the output as `baltimore_glm` so that we can apply `broom::tidy` to this object and obtain the estimate and confidence interval of the adjusted odds ratio for solving homicides comparing non-white victims to white victims.

```{r q1_glm_baltimore}
baltimore_glm = 
  filter(homicide_df, city_state == "Baltimore, MD") |> 
  glm(resolution ~ victim_age + victim_sex + victim_race, family = binomial(), data = _)

baltimore_glm |> 
  broom::tidy() |> 
  mutate(
    OR = exp(estimate), 
    OR_CI_upper = exp(estimate + 1.96 * std.error),
    OR_CI_lower = exp(estimate - 1.96 * std.error)) |> 
  filter(term == "victim_sexMale") |> 
  select(OR, OR_CI_lower, OR_CI_upper) |>
  knitr::kable(digits = 3)
```

Below, by incorporating `nest()`, `map()`, and `unnest()` into the preceding Baltimore-specific code, we fit a model for each of the cities, and extract the adjusted odds ratio (and CI) for solving homicides comparing non-white victims to white victims. We show the first 5 rows of the resulting dataframe of model results.

```{r q1_glm_all_cities}
model_results = 
  homicide_df |> 
  nest(data = -city_state) |> 
  mutate(
    models = map(data, \(df) glm(resolution ~ victim_age + victim_sex + victim_race, 
                             family = binomial(), data = df)),
    tidy_models = map(models, broom::tidy)) |> 
  select(-models, -data) |> 
  unnest(cols = tidy_models) |> 
  mutate(
    OR = exp(estimate), 
    OR_CI_upper = exp(estimate + 1.96 * std.error),
    OR_CI_lower = exp(estimate - 1.96 * std.error)) |> 
  filter(term == "victim_sexMale") |> 
  select(city_state, OR, OR_CI_lower, OR_CI_upper)

model_results |>
  slice(1:5) |> 
  knitr::kable(digits = 3)
```
Below we generate a plot of the estimated ORs and CIs for each city, ordered by magnitude of the OR from smallest to largest. From this plot we see that most cities have odds ratios that are smaller than 1, suggesting that crimes with male victims have smaller odds of resolution compared to crimes with female victims after adjusting for victim age and race. This disparity is strongest in New yrok. In roughly half of these cities, confidence intervals are narrow and do not contain 1, suggesting a significant difference in resolution rates by sex after adjustment for victim age and race. 

```{r q1_plot}
model_results |> 
  mutate(city_state = fct_reorder(city_state, OR)) |> 
  ggplot(aes(x = city_state, y = OR)) + 
  geom_point() + 
  geom_errorbar(aes(ymin = OR_CI_lower, ymax = OR_CI_upper)) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

# Problem 2

```{r message=FALSE}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2022-01-01",
    date_max = "2022-12-31") |>
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) |>
  select(name, id, everything())
```

```{r}
lm(tmax ~ tmin + prcp, data = weather_df)

boot_sample = function(df) {
  sample_frac(df, replace=TRUE)
}

boot_straps = 
  tibble(strap_number = 1:5000) %>% 
  mutate(
    strap_sample = map(strap_number, ~boot_sample(df = weather_df))
  )

boot_straps %>% 
  slice(1:3) %>% 
  mutate(strap_sample = map(strap_sample, arrange, tmax)) %>%  
  pull(strap_sample)
```

```{r}
bootstrap_results = 
  boot_straps %>% 
  mutate(
    models = map(strap_sample, ~lm(tmax ~ tmin + prcp, data = .)
  ), 
    results = map(models, broom::tidy),
    r_squared = map_dbl(models, ~broom::glance(.x)$r.squared),
    log_beta = map_dbl(models, ~ {
      coef <- coefficients(.x)
      if (coef[2] * coef[3] >= 0) log(coef[2] * coef[3]) else NA_real_
    })
  ) %>% 
  select(-strap_sample, -models) %>% 
  unnest(results)

```

## Plotting the distributions of estimates for r_squared and log_beta

```{r}
estimate_plot_rs = 
bootstrap_results %>% 
  ggplot(aes(x = r_squared)) + geom_density()

estimate_plot_rs
```

The distribution of the r sqaured estimates appears approximately normal but may have a slight left skew. This slight skew is likely due to random sampling variability. 

```{r}
estimate_plot_log = 
bootstrap_results %>% 
  ggplot(aes(x = log_beta)) + geom_density()

estimate_plot_log
```

The distribution of the log(beta_1*beta_2) estimates is strongly left skewed. This may be due to the fact that there were several negative beta estimates that could not be used in the log calculations, indicating that this may not be representative of the dataset the bootstrap was performed on. 

## Identifying 95% Confidence Intervals

```{r}
bootstrap_results %>%  
  summarize(
    ci_lower = quantile(r_squared, 0.025), 
    ci_upper = quantile(r_squared, 0.975))
```

We are 95% confident that the true r-squared value is between 0.889 and 0.941.

```{r}
bootstrap_results %>%  
  summarize(
    ci_lower = quantile(log_beta, 0.025, na.rm = TRUE), 
    ci_upper = quantile(log_beta, 0.975, na.rm = TRUE))
```

We are 95% confident that the true log(beta_1*beta_2) value is between -8.98 and -4.60. 

# Problem 3 

## Tidying the data
```{r}
birthweight_df = 
  read_csv("data/birthweight.csv") %>% 
  janitor::clean_names() %>% 
  mutate(across(c(babysex, frace, malform, mrace), as_factor)) %>% 
  select(-pnumsga, -pnumlbw)

missing_val_check = 
  birthweight_df %>% 
  summarise_all(~sum(is.na(.)))
```

## Regression model

```{r}
all_fit = lm(bwt~ ., data = birthweight_df)

step(all_fit, direction = "both")
```

```{r}
fit = lm(bwt ~ babysex + bhead + blength + delwt + fincome + 
    gaweeks + mheight + mrace + parity + ppwt + smoken, data = birthweight_df)
```

Final model: lm( bwt ~ babysex + bhead + blength + delwt + fincome + gaweeks + mheight + mrace + parity + ppwt + smoken, data = birthweight_df)

I chose to use a stepwise compariosn of the model for the building process to determine the final regression model. The final model is a linear regression model that contains eleven predictors with the outcome variable birthweight. 

```{r}
birthweight_df %>% 
  modelr::add_residuals(fit) %>% 
  modelr::add_predictions(fit) %>% 
  ggplot(aes(x = fitted.values(fit), y = residuals(fit))) + geom_point()
```
There does not appear to be any distinct pattern in the residual plot. 

## Cross Validation 

Original model: 

fit = lm(bwt ~ babysex + bhead + blength + delwt + fincome + gaweeks + mheight + mrace + parity + ppwt + smoken, data = birthweight_df)
  
Comparison models: 

fit_main = lm(bwt ~ blength + gaweeks, data = birthweight_df)

fit_int = lm(bwt ~ bhead + blength + babysex + babysex*bhead + babysex*blength + bhead*blength + babysex*bhead*blength, data = birthweight_df)

```{r}
fit_main = lm(bwt ~ blength + gaweeks, data = birthweight_df)

fit_int = lm(bwt ~ bhead + blength + babysex + babysex*bhead + babysex*blength + bhead*blength + babysex*bhead*blength, data = birthweight_df)
```

## CV plot

```{r}
cv_df =
  crossv_mc(birthweight_df, 100) |> 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble))

cv_df = 
  cv_df |> 
  mutate(
    fit = map(train, \(df) lm(bwt ~ babysex + bhead + blength + delwt + fincome + gaweeks + mheight + mrace + parity + ppwt + smoken, data = birthweight_df)),
    fit_main = map(train, \(df) lm(bwt ~ blength + gaweeks, data = birthweight_df)),
    fit_int  = map(train, \(df) lm(bwt ~ bhead + blength + babysex + babysex*bhead + babysex*blength + bhead*blength + babysex*bhead*blength, data = birthweight_df))) |> 
  mutate(
    rmse_fit = map2_dbl(fit, test, \(mod, df) rmse(model = mod, data = df)),
    rmse_main = map2_dbl(fit_main, test, \(mod, df) rmse(model = mod, data = df)),
    rmse_int = map2_dbl(fit_int, test, \(mod, df) rmse(model = mod, data = df)))

cv_df |> 
  select(starts_with("rmse")) |> 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") |> 
  mutate(model = fct_inorder(model)) |> 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```

Looking at the prediction error distributions for all three mdoels, it appears that the orginal model that I fitted is the best of the three models. Second to this, I would use the third model that includes the interaction terms. This is based on the most common rmse values for each model as is seen in the violin plot above. 
