---
title: "hw6"
output: github_document
date: "2023-11-29"
---

```{r setup, include=FALSE}
library(tidyverse)
library(p8105.datasets)
library(modelr)
library(mgcv)

set.seed(1)
```

# Problem 1 

# Problem 2

```{r message=FALSE}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2022-01-01",
    date_max = "2022-12-31") |>
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) |>
  select(name, id, everything())
```

```{r}
lm(tmax ~ tmin + prcp, data = weather_df)

boot_sample = function(df) {
  sample_frac(df, replace=TRUE)
}

boot_straps = 
  tibble(strap_number = 1:5000) %>% 
  mutate(
    strap_sample = map(strap_number, ~boot_sample(df = weather_df))
  )

boot_straps %>% 
  slice(1:3) %>% 
  mutate(strap_sample = map(strap_sample, arrange, tmax)) %>%  
  pull(strap_sample)
```

```{r}
bootstrap_results = 
  boot_straps %>% 
  mutate(
    models = map(strap_sample, ~lm(tmax ~ tmin + prcp, data = .)
  ), 
    results = map(models, broom::tidy),
    r_squared = map_dbl(models, ~broom::glance(.x)$r.squared),
    log_beta = map_dbl(models, ~ {
      coef <- coefficients(.x)
      if (coef[2] * coef[3] >= 0) log(coef[2] * coef[3]) else NA_real_
    })
  ) %>% 
  select(-strap_sample, -models) %>% 
  unnest(results)

```

## Plotting the distributions of estimates for r_squared and log_beta

```{r}
estimate_plot_rs = 
bootstrap_results %>% 
  ggplot(aes(x = r_squared)) + geom_density()

estimate_plot_rs
```

```{r}
estimate_plot_log = 
bootstrap_results %>% 
  ggplot(aes(x = log_beta)) + geom_density()

estimate_plot_log
```

Use 5000 bootstrap samples and, for each bootstrap sample, produce estimates of these two quantities. Plot the distribution of your estimates, and describe these in words.


Using the 5000 bootstrap estimates, identify the 2.5% and 97.5% quantiles to provide a 95% confidence interval for r̂ 2
 and log(β̂ 0∗β̂ 1)



# Problem 3 